Intentional release of native species undermines ecological stability

### 2022-09-27 rmd/supporting_info.Rmd
Update supporting_info.Rmd

## mcmc sample size
df_mcmc_ssm <- list.files(path = here::here("data_fmt"),
                    full.names = T,
                    pattern = "joint") %>% 
  readRDS() %>% 
  ungroup() %>% 
  dplyr::select(n_total_mcmc,
                n_sample,
                n_thin,
                n_burn) %>% 
  distinct()

df_mcmc_reg <- list.files(path = here::here("output"),
                          full.names = T,
                          pattern = "summary_reg") %>% 
  readRDS() %>% 
  dplyr::select(n_total_mcmc,
                n_sample,
                n_thin,
                n_burn) %>% 
  distinct()

df_mcmc_ssm <- list.files(path = here::here("data_fmt"),
                    full.names = T,
                    pattern = "joint") %>% 
  readRDS() %>% 
  ungroup() %>% 
  dplyr::select(n_total_mcmc,
                n_sample,
                n_thin,
                n_burn) %>% 
  distinct()

df_mcmc_ricker <- list.files(path = here::here("output"),
                             full.names = T,
                             pattern = "summary_multi_ricker") %>% 
  readRDS() %>% 
  dplyr::select(n_total_mcmc,
                n_sample,
                n_thin,
                n_burn) %>% 
  distinct()

>>>>

## mcmc sample size

df_mcmc <- lapply(c("summary_joint", "summary_reg", "summary_multi_ricker"),
       function(x) {
         list.files(path = here::here("output"),
                    full.names = T,
                    pattern = x) %>% 
           readRDS() %>% 
           ungroup() %>% 
           dplyr::select(n_total_mcmc,
                         n_sample,
                         n_thin,
                         n_burn) %>% 
           distinct() %>% 
           mutate(model = str_extract(x, "joint|reg|ricker"))
       }) %>% 
  bind_rows()
